Tor's Usability for Censorship Circumvention

### 2015-12-11 paper/circumvention-experiment.tex

\begin{figure*}[t]
\label{fig:interface}
  \centering
    \includegraphics[width=\textwidth]{../torconfig.png}
    \caption{This flow chart shows all of the possible paths taken through the
    Tor configuration interface. A state represents a window in the interface,
    with the exception of the leaves, which indicate the final action taken by
    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
    transitions between the states indicate which user action causes that
    transition. Annotations for the error states can be found by following
\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{this hyperlink}.}
\end{figure*}

@@

\begin{figure}[t]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface.}
\end{figure}

@@

\subsection{Interface design and iteration}
After completing the qualitative user studies, we analyzed the results to
identify common themes and problems. These were the basis of our interface 
redesign. To do this, we used an iterative design process, starting with low-fidelity
(paper and pencil) prototypes and then proceeding to higher-fidelity (realistic clickable mockups)
prototypes.We collected feedback from researchers, professors, and Tor users and developers
through the Tor project's mailing lists. We then iterated on the design by
incorporating the comments and suggestions we received into the next version of
the interface. We plan to take some qualitative measurements of the new design
by having some participants think aloud while they use our realistic mockup. This is 
to get any feedback before we launch our quantitative interface evaluation.

@@

\begin{figure}[t]
\label{fig:error}
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\end{figure}

@@

\begin{figure}[t]
\label{fig:redesign-bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-bridges.png}
    \caption{the bridge selection screen, with the option to ``Add Custom
    Bridge''}
\end{figure}

A progress indicator at the top of the window indicates various steps necessary
for configuring a connection. In addition to communicating to the user what the various 
steps of configuration are from the beginning, this indicator also serves to clarify the independence of
bridges and proxies, which need to be configured separately. In the event of a failure, the user is
returned to the first step of the process -- the bridge configuration -- to
avoid misleading users into thinking the proxy settings are the culprit. Previously,
the user had to manually click to go backward in the dialog to configure bridges.
Even in the rare event that the proxy is the issue for the connection setting, the user
will be directed to the proxy page naturally through the flow of the UI. \\

@@

\begin{figure}[t]
\label{fig:markov}
  \centering
    \includegraphics[width=0.5\textwidth]{markov.png}
    \caption{An illustration on a planned analysis using the quantitative survey data. This illustration shows two possible user interfaces and uses a Markov model to reflect the aggregate user behavior. We believe that this will be an concrete way to predict user behaviors, which is valuable feedback for if the interface is guiding users in a desired UI path.}
\end{figure}

\begin{figure}[t]
\label{fig:bar}
  \centering
    \includegraphics[width=0.5\textwidth]{screen-bar.png}
    \caption{An illustration of how we plan to visualize large-scale UI flows as a succinct way to display all participants' window traversal. We plan to color code the screens so that the reader can see trends at a glance, such as how the UI path for participants in a mild censorship environment with the old design compare to the UI flow for the participants in a mild censorship environment with a new design. It also can communicate how much work was required of a user to configure a connection.}
\end{figure}

@@

\begin{figure}[h]
\label{fig:window1}
  \centering
    \includegraphics[width=0.5\textwidth]{window1.png}
    \caption{Window 1: the first configuration window shown to the user upon
    starting Tor Browser for the first time. Note that the interface's default choice
    is to connect directly through Tor. The interface also gives additional guidance
    to help users answer this question.}
\end{figure}

\begin{figure}[h]
\label{fig:window2}
  \centering
    \includegraphics[width=0.5\textwidth]{window2.png}
    \caption{Window 2: This is the next window shown if a user chooses to configure 
    bridges or proxies. Note that the interface's default answer is ``No,'' 
    and also advises users to click ``No'' if they are unsure. The user can navigate to the 
    previous window by clicking ``Go Back,'' and continue configuration by clicking 
    ``Continue.''}
\end{figure}

\begin{figure}[h]
\label{fig:window3}
  \centering
    \includegraphics[width=0.5\textwidth]{window3.png}
    \caption{Window 3: This is the window shown when a user answers that a bridge 
    is required for the connection. Note that the default answer is to connect with a hard-
    coded bridge rather than to enter in a custom bridge, and to use the recommended 
    transport (obfs3). A possible source of confusion is that that the user is asked to choose 
    a transport type, when the interface clearly is asking for bridge configuration. The user 
    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
    by clicking  ``Continue.''}
\end{figure}

\begin{figure}[h]
\label{fig:window4}
  \centering
    \includegraphics[width=0.5\textwidth]{window4.png}
    \caption{Window 4: This is the window shown after a user has deemed that a bridge
    is not required for the connection, or when the bridge configuration settings have been 
    chosen. Note that the default answer to if the user requires a proxy is ``No.'' Additionally,
    there is text to guide the users on how to answer this question. The user 
    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
    by clicking  ``Continue.''}
\end{figure}

\begin{figure}[h]
\label{fig:window5}
  \centering
    \includegraphics[width=0.5\textwidth]{window5.png}
    \caption{Window 5: This is the window shown when a user answers that a proxy is 
    required for the connection. Note that there are no default values in the answers, 
    where there were for bridges. Additionally, since this is the last window in the configuration
    interface, the options to navigate to other windows are to simply ``go back,'' or to 
    connect to the Tor Network.}
\end{figure}
\end{document}

>>>>

\begin{figure*}[t]
  \centering
    \includegraphics[width=\textwidth]{../torconfig.png}
    \caption{This flow chart shows all of the possible paths taken through the
    Tor configuration interface. A state represents a window in the interface,
    with the exception of the leaves, which indicate the final action taken by
    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
    transitions between the states indicate which user action causes that
    transition. Annotations for the error states can be found by following
\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{this hyperlink}.}
\label{fig:interface}
\end{figure*}

@@

\begin{figure}[t]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface.}
\label{fig:bridges}
\end{figure}

@@

\subsection{Interface design and iteration}
After completing the qualitative user studies, we analyzed the results to
identify common themes and problems. These were the basis of our interface 
redesign. To do this, we used an iterative design process, starting with low-fidelity
(paper and pencil) prototypes and then proceeding to higher-fidelity (realistic clickable mockups)
prototypes.

We collected feedback from researchers, professors, and Tor users and developers
through the Tor project's mailing lists. We then iterated on the design by
incorporating the comments and suggestions we received into the next version of
the interface. We plan to take some qualitative measurements of the new design
by having some participants think aloud while they use our realistic mockup. This is 
to get any feedback before we launch our quantitative interface evaluation.

@@

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\label{fig:error}
\end{figure}

@@

\begin{figure}[t]
\label{fig:redesign-bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-bridges.png}
    \caption{the bridge selection screen, with the option to ``Add Custom
    Bridge''}
\label{fig:redesign-bridges}
\end{figure}

A progress indicator at the top of the window indicates various steps necessary
for configuring a connection. In addition to communicating to the user what the various 
steps of configuration are from the beginning, this indicator also serves to clarify the independence of
bridges and proxies, which need to be configured separately. In the event of a failure, the user is
returned to the first step of the process -- the bridge configuration -- to
avoid misleading users into thinking the proxy settings are the culprit. Previously,
the user had to manually click to go backward in the dialog to configure bridges.
In the rare event that the proxy is the issue for the connection setting, the user
will be directed to the proxy page naturally through the flow of the UI. \\

@@

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{markov.png}
    \caption{An illustration on a planned analysis using the quantitative survey data. This illustration shows two possible user interfaces and uses a Markov model to reflect the aggregate user behavior. We believe that this will be an concrete way to predict user behaviors, which is valuable feedback for if the interface is guiding users in a desired UI path.}
\label{fig:markov}
\end{figure}

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{screen-bar.png}
    \caption{An illustration of how we plan to visualize large-scale UI flows as a succinct way to display all participants' window traversal. We plan to color code the screens so that the reader can see trends at a glance, such as how the UI path for participants in a mild censorship environment with the old design compare to the UI flow for the participants in a mild censorship environment with a new design. It also can communicate how much work was required of a user to configure a connection.}
\label{fig:bar}
\end{figure}

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.5\textwidth]{window1.png}
    \caption{Window 1: the first configuration window shown to the user upon
    starting Tor Browser for the first time. Note that the interface's default choice
    is to connect directly through Tor. The interface also gives additional guidance
    to help users answer this question.}
\label{fig:window1}
\end{figure}

\begin{figure}[h]
  \centering
    \includegraphics[width=0.5\textwidth]{window2.png}
    \caption{Window 2: This is the next window shown if a user chooses to configure 
    bridges or proxies. Note that the interface's default answer is ``No,'' 
    and also advises users to click ``No'' if they are unsure. The user can navigate to the 
    previous window by clicking ``Go Back,'' and continue configuration by clicking 
    ``Continue.''}
\label{fig:window2}
\end{figure}

\begin{figure}[h]
  \centering
    \includegraphics[width=0.5\textwidth]{window3.png}
    \caption{Window 3: This is the window shown when a user answers that a bridge 
    is required for the connection. Note that the default answer is to connect with a hard-
    coded bridge rather than to enter in a custom bridge, and to use the recommended 
    transport (obfs3). A possible source of confusion is that that the user is asked to choose 
    a transport type, when the interface clearly is asking for bridge configuration. The user 
    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
    by clicking  ``Continue.''}
\label{fig:window3}
\end{figure}

\begin{figure}[h]
  \centering
    \includegraphics[width=0.5\textwidth]{window4.png}
    \caption{Window 4: This is the window shown after a user has deemed that a bridge
    is not required for the connection, or when the bridge configuration settings have been 
    chosen. Note that the default answer to if the user requires a proxy is ``No.'' Additionally,
    there is text to guide the users on how to answer this question. The user 
    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
    by clicking  ``Continue.''}
\label{fig:window4}
\end{figure}

\begin{figure}[h]
  \centering
    \includegraphics[width=0.5\textwidth]{window5.png}
    \caption{Window 5: This is the window shown when a user answers that a proxy is 
    required for the connection. Note that there are no default values in the answers, 
    where there were for bridges. Additionally, since this is the last window in the configuration
    interface, the options to navigate to other windows are to simply ``go back,'' or to 
    connect to the Tor Network.}
\label{fig:window5}
\end{figure}
\end{document}
